% Zhihao (Vincent) Zheng - Curriculum Vitae
% Email: zhihao.zheng@mail.mcgill.ca
% Web: https://vincent-zheng.com/
% Repo: https://github.com/rottenivy/cv

\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[strict,autostyle]{csquotes}
\usepackage[USenglish]{babel}
\usepackage{microtype}
\usepackage{datetime}
\usepackage{tabto}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{setspace}

\newcommand{\myname}{Zhihao (Vincent) Zheng}

\usepackage{crimson}
\usepackage{helvet}

\newcommand{\listtabwidth}{1.75cm}
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

\SetTracking{encoding=T1, family=\sfdefault}{50}
\titleformat{\section}{\sffamily\small\bfseries\lsstyle\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{24pt plus 4pt minus 2pt}{12pt plus 2pt minus 2pt}
\titleformat{\subsection}{\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{12pt plus 4pt minus 2pt}{8pt plus 2pt minus 2pt}

\geometry{body={6.5in, 9.0in}, left=1.0in, top=1.0in}
\setlength\parindent{0em}
\setstretch{0.9}
\newcommand{\listitemspace}{0.25em}

\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {probabilistic machine learning, time series forecasting, uncertainty quantification, traffic data science},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright

    \namefont{\myname}

    \vspace{1em}
    \begin{minipage}[t]{0.64\textwidth}
        Faculty of Engineering \\
        McGill University
    \end{minipage}
    \begin{minipage}[t]{0.35\textwidth}
        Email: \href{mailto:zhihao.zheng@mail.mcgill.ca}{zhihao.zheng@mail.mcgill.ca} \\
        Phone: +1 (438) 941-6646 \\
        Web: \href{https://vincent-zheng.com/}{https://vincent-zheng.com/}
    \end{minipage}
    \vspace{0.5em}

    \section*{Education}
    \begin{tablist}
        \item[Ph.D.] \tab Civil Engineering (Machine learning \& Statistics), McGill University, Canada, 2021 - expected 2025
        \item \tab {\footnotesize\textit{Thesis: ``Probabilistic Time Series Forecasting with Correlated Errors''}}
        \item[M.S.]  \tab Transportation Engineering (Network Science), Central South University, China, 2020
        \item \tab {\footnotesize\textit{Thesis: ``Understanding Coupling Dynamics of Public Transportation Systems''}}
        \item[B.E.]  \tab Transportation Engineering, Central South University, China, 2017 \textbf{(Rank: 3/116)}
    \end{tablist}

    \section*{Research Areas}
    Probabilistic ML · Generative Modeling · Uncertainty Quantification · Sequential/Multimodal Data

    \section*{Technical Skills}
    Python · PyTorch · NumPy/Pandas · Git · Docker

    \section*{Selected Publications}
    \subsection*{Preprints}
    \begin{tablist}
        \item[2024] \tab \textbf{Zheng, Z.} and Sun, L. \enquote{MVG-CRPS: A Robust Loss Function for Multivariate Probabilistic Forecasting.} \textit{arXiv preprint} \href{https://arxiv.org/abs/2410.09133}{arXiv:2410.09133}
    \end{tablist}

    \subsection*{Peer-Reviewed Articles}
    \begin{tablist}
        \item[2025] \tab \textbf{Zheng, Z.}, Choi, S. and Sun, L. \enquote{Probabilistic Traffic Forecasting with Dynamic Regression.} \textit{Transportation Science} \href{https://pubsonline.informs.org/doi/abs/10.1287/trsc.2024.0560}{doi:10.1287/trsc.2024.0560}
        \item[2024] \tab \textbf{Zheng, Z.} and Sun, L. \enquote{Multivariate Probabilistic Time Series Forecasting with Correlated Errors.} In \textit{Proceedings of the 38th Conference on Neural Information Processing Systems} (\textbf{NeurIPS 2024}) \href{https://papers.nips.cc/paper_files/paper/2024/file/619b8e3ead58dce90bc615f2a7d5d102-Paper-Conference.pdf}{[pdf]}
        \item[2024] \tab \textbf{Zheng, Z.}, Choi, S., and Sun, L. \enquote{Better Batch for Deep Probabilistic Time Series Forecasting}. \textit{International Conference on Artificial Intelligence and Statistics} (\textbf{AISTATS 2024}) vol. 238:91--99. PMLR. \href{https://proceedings.mlr.press/v238/zheng24a.html}{[pdf]}
        \item[2021] \tab \textbf{Zheng, Z.}, Ling, X., Wang, P., Xiao, J. and Zhang, F. \enquote{A Hybrid Model for Predicting Anomalous Large Passenger Flow in Urban Metros.} \textit{IET Intelligent Transport Systems} 14 (14), 1987--1996. \href{https://doi.org/10.1049/iet-its.2020.0054}{doi:10.1049/iet-its.2020.0054}
        \item[2018] \tab \textbf{Zheng, Z.}, Huang, Z., Zhang, F. and Wang, P. \enquote{Understanding Coupling Dynamics of Public Transportation.} \textit{EPJ Data Science} 7, 23. \href{https://doi.org/10.1140/epjds/s13688-018-0148-6}{doi:10.1140/epjds/s13688-018-0148-6}
        \item[2018] \tab \textbf{Zheng, Z.}, Wu, W., Chen, X., Hu, R., Liu, X. and Wang, P. \enquote{A Traffic Sensing and Analyzing System Using Social Media Data.} \textit{Acta Automatica Sinica} 44 (4), 656--666. \href{http://dx.doi.org/10.16383/j.aas.2017.c160537}{doi:10.16383/j.aas.2017.c160537}
    \end{tablist}

    \textit{Complete bibliography:} \href{https://scholar.google.com/citations?hl=en&user=h2Et54sAAAAJ&view_op=list_works&sortby=pubdate}{Google Scholar}

    \section*{Teaching Experience}
    \begin{tablist}
        \item[Fall 2024] TA, CIVE 440 Traffic Engineering and Simulation, McGill University
        \item[Winter 2024] TA, CIVE 542 Transportation Network Analysis, McGill University
        \item[Fall 2023] TA, CIVE 440 Traffic Engineering and Simulation, McGill University
        \item[Winter 2023] TA, CIVE 542 Transportation Network Analysis, McGill University
        \item[Winter 2022] TA, CIVE 319 Transportation Engineering, McGill University
    \end{tablist}

    \section*{Invited Talks}
    \begin{tablist}
        \item[2018] \tab \enquote{Research Paper Done Right.} School of Traffic and Transportation Engineering, Central South University. Graduate Student Academic Seminar Series. Changsha, China. Oct 31.
    \end{tablist}

    \section*{Conference Activity}
    \subsection*{Conference Presentation}
    \begin{tablist}
        \item[2024] \tab  \enquote{Better Batch for Deep Probabilistic Time Series Forecasting.} The 27th International Conference on Artificial Intelligence and Statistics (AISTATS 2024). València, Spain. May 2--4. (Poster)
        \item[2024] \tab  \enquote{Deep Probabilistic Traffic Forecasting with Correlated Errors.} 2024 Transportation Research Board 103rd Annual Meeting (TRB 2024). Washington, DC. Jan 7--11. (Poster)
        \item[2023] \tab  \enquote{Dynamic Modes as Time Representation for Traffic Time Series Forecasting.} 2023 Transportation Research Board 102nd Annual Meeting (TRB 2023). Washington, DC. Jan 7--11. (Poster)
        \item[2018] \tab  \enquote{Coupling Dynamics of Multiplex Public Transportation Networks and Multimodal Urban Mobility.} 2018 Chinese Conference on Complex Network (CCCN 2018). Chongqing, China. Oct 12--15. (Oral)
        \item[2018] \tab  \enquote{Statistical Analysis of Traffic-Related Social Media Data in China.} 2018 International Conference of Applications and Techniques in Cyber Intelligence (ATCI 2018). Shanghai, China. Jul 11--13. (Oral)
    \end{tablist}

    \section*{Internship}
    \begin{tablist}
        \item[2021] \tab  Mitacs with ExPretio Technologies, "Adaptive multi-horizon models for probabilistic demand forecasting".
    \end{tablist}

    \section*{Grants and Awards}
    \subsection*{Awards and Honors}
    \begin{tablist}
        \item[2023] \tab Graduate Research Enhancement and Travel Awards (G.R.E.A.T.) (CA\$500)
        \item[2020] \tab 2020 Outstanding Graduates of Hunan Province, China (1\%)
        \item[2019] \tab 2nd Prize, China Postgraduate Mathematical Contest in Modeling (13\%)
        \item[2019] \tab 2018--2019 Central South University Outstanding Student Award (5\%)
        \item[2018] \tab 2017--2018 Central South University Outstanding Student Award (5\%)
        \item[2017] \tab 2017 Outstanding Graduates of Hunan Province, China (1\%)
        \item[2016] \tab 1st Prize, National Competition of Transportation Science and Technology, Ministry of Education of China (2\%)
        \item[2016] \tab 2015--2016 Central South University Outstanding Student Award (5\%)
        \item[2015] \tab 2014--2015 Central South University Outstanding Student Award (5\%)
        \item[2014] \tab 2013--2014 Central South University Outstanding Student Award (5\%)
    \end{tablist}

    \subsection*{Scholarships}
    \begin{tablist}
        \item[2018] \tab National Scholarship for Graduate Students, Ministry of Education of China (¥20,000) (0.1\%)
        \item[2016] \tab National Scholarship for Outstanding Students Majoring in Transportation Engineering (¥5,000) (0.8\%)
        \item[2016] \tab Central South University 2nd Class Academic Scholarship (¥1,500)
        \item[2015] \tab Central South University 1st Class Academic Scholarship (¥2,000)
        \item[2015] \tab Xinheng Corporation Xinheng Education Scholarship (¥10,000)
        \item[2014] \tab Central South University 2nd Class Academic Scholarship (¥1,500)
    \end{tablist}

    \subsection*{Grants and Fellowships}
    \begin{tablist}
        \item[2022--23] \tab McGill Graduate Excellence Fellowship (GEF) (CA\$5,000)
        \item[2022--26] \tab FRQNT B2X PhD Scholarship (CA\$21,000/year)
        \item[2021--24] \tab McGill Engineering Doctoral Award (MEDA) (CA\$37,000/year)
        \item[2019--22] \tab Large Crowd Gathering Mechanism, Early Warning and Management Method Based on Multi-Source Big Data Fusion (¥480,000). National Natural Science Foundation of China. Student Participant.
        \item[2017--20] \tab Central South University Graduate Fellowship (¥16,000/year)
        \item[2016--17] \tab A Traffic Events Detection System Based on Social Media Data (¥3,000). Central South University. Co-PI.
        \item[2015--16] \tab A Traffic Signal System for Blind Pedestrians Based on Smart Wristbands (¥20,000). National Students’ Innovation and Entrepreneurship Training Program of China. PI.
    \end{tablist}

    \section*{Service}
    \subsection*{Academic Journal Peer Review}
    \begin{itemize}
        \item \textit{International Journal of Data Science and Analytics}
        \item \textit{Scientific Reports}
        \item \textit{Knowledge and Information Systems}
        \item \textit{Transportation Research Part C: Emerging Technologies}
        \item \textit{IEEE Transactions on Intelligent Transportation Systems}
        \item \textit{Journal of Computational Science}
        \item \textit{Journal of Advanced Transportation}
        \item \textit{Chinese Journal of Computers}
    \end{itemize}

    \subsection*{Conference Peer Review}
    \begin{itemize}
        \item NeurIPS 2024 Workshop TSALM
        \item IEEE Conference on Intelligent Transportation Systems (ITSC)
        \item Transportation Research Board Annual Meeting (TRB)
    \end{itemize}

    \begin{center}
        \vfill
        Updated \monthyeardate\today
    \end{center}

\end{document}
